Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-12-29 Paper.Rmd
i am hoping this is the last

The existence of the Negativity Bias and how the potential effects of Negativity Bias on Review Helpfulness could be moderated by either Search And Experience goods will be the main focus of this study. A lesser degree of Negativity Bias is expected for Experience Goods. Additionally, the amount of information that a review has and its connection to Review Helpfulness with respect to Review Ratings will be analyzed. Next, the diagnostic values of the negative and positive sentiments are going to be discussed. Because of the Negativity Bias, a positive relationship between Negative Sentiments and Review Helpfulness is expected. Lastly, the relationship between the Review Helpfulness and the timeline of a review will be inquired.

@@

***H5**: There is a positive relationship between the Proportion of Negative Words and the Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
***H6**: There is a negative relationship between the Proportion of Positive Words and the Perceived Helpfulness for both product types.*

@@

Tobit regression results are presented at Table \@ref(tab:Reg-Results-Tobit) alongside with OLS results as a benchmark at Table \@ref(tab:Reg-Results-OLS) [@mudambi2010; @kuan2015; @choi2020].

>>>>

The existence of the Negativity Bias and how the potential effects of Negativity Bias on Review Helpfulness could be moderated by either Search And Experience goods will be the main focus of this study. A lesser degree of Negativity Bias is expected for Experience Goods. Additionally, the amount of information that a review has and its connection to Review Helpfulness with respect to Review Ratings will be analyzed. Next, the diagnostic values of the negative and positive sentiments are going to be discussed. Because of the Negativity Bias, a positive relationship between Negative Sentiments and Review Helpfulness is expected. Lastly, the positive relationship between the Review Helpfulness and the timeline of a review will be inquired because an updated and new information might be more helpful than an old information.

@@

***H5**: There is a positive relationship between the Proportion of Negative Words and the Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*

@kuan2015 discussed that since the majority of the reviews are positive these positive reviews lose their diagnostic values for a given product. Compared to negative information which may lay out potential risks for the product in a much more objective sense, positive information might be found more subjective and lay out a more ambiguous information about the product which may confuse potential consumers. Therefore, it is hypothesized that:

\
***H6**: There is a negative relationship between the Proportion of Positive Words and the Perceived Helpfulness for both product types.*

@@

Tobit regression results are presented at Table \@ref(tab:Reg-Results-Tobit) alongside with OLS results as a benchmark at Table \@ref(tab:Reg-Results-OLS) [@mudambi2010; @kuan2015; @choi2020]. Both Tobit regression results and OLS results have the same signs and significances which might indicate that the results are somewhat robust. For Search goods, the magnitudes of the coefficients are usually higher . This is quite expected since Search good data has more censored observations compared to Experience goods data.
